---
title: "JITAI Meta-Analysis"
subtitle: "1. Data Cleaning"
author: "Constantin Yves Plessen"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: show
    highlight: pygment
    keep_md: no
    theme: lumen
    toc: yes
    toc_depth: 3
    toc_float: yes
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(janitor)
library(tidyverse)
library(metapsyTools)
library(esc)
library(metafor)
library(skimr)
```

# Setup

## Load data

```{r}
jitai_df <- readxl::read_excel("data/raw/Daten von Yves Github_ps_cs_V2_cyp.xlsx") %>% 
  clean_names() %>% 
  select(es_id, study_id, study, 
       outcome_measure, intervention_group, control_group, sample, device,  sr_clinician, time, 
       post_m_ig:change_n_cg,
       everything(),
       -c(es, se, yi, vi)) %>% 
  glimpse() 
```

## Calculate effect sizes

### Transform se to sd
https://handbook-5-1.cochrane.org/chapter_7/7_7_3_2_obtaining_standard_deviations_from_standard_errors_and.htm 
```{r}
jitai_df_clean <- jitai_df %>% 
  mutate_at(vars(post_m_ig:change_n_cg), as.numeric) %>% 
  mutate(post_sd_ig = ifelse(!is.na(post_se_ig), post_se_ig * sqrt(post_n_ig), post_sd_ig),
         post_sd_cg = ifelse(!is.na(post_se_cg), post_se_cg * sqrt(post_n_cg), post_sd_cg),
         
         baseline_sd_ig = ifelse(!is.na(baseline_se_ig), baseline_se_ig * sqrt(baseline_n_ig), baseline_sd_ig),
         baseline_sd_cg = ifelse(!is.na(baseline_se_cg), baseline_se_cg * sqrt(baseline_n_cg), baseline_sd_cg))  %>% 
  
  mutate(change_sd_ig = sqrt(change_n_ig) * (change_ig_ci_upper - change_ig_ci_lower) /3.92,
         change_sd_cg = sqrt(change_n_cg) * (change_cg_ci_upper - change_cg_ci_lower) /3.92,
  )
```


### Calculate Hedges g from means, sd, and n
```{r}
meanSD = function(x, ...){
  x %>%
    purrr::pmap_dfr(function(post_m_ig,
                             post_sd_ig,
                             post_n_ig,
                             post_m_cg,
                             post_sd_cg,
                             post_n_cg, ...)
    {esc::esc_mean_sd(post_m_ig,
                      post_sd_ig,
                      post_n_ig,
                      post_m_cg,
                      post_sd_cg,
                      post_n_cg,
                      es.type = "g") %>%
        as.data.frame()  %>% dplyr::select(es, se) %>%
        suppressWarnings()})
}

jitai_es_meanSD <- jitai_df_clean %>% 
  meanSD()
```

### Calculate Hedges g from change scores
```{r}
changeES = function(x, ...){
  x %>%
    purrr::pmap_dfr(function(change_m_ig, change_m_cg, change_sd_ig,
                             change_sd_cg, change_n_ig, change_n_cg, ...)
    {esc::esc_mean_sd(change_m_ig, change_sd_ig, change_n_ig,
                      change_m_cg, change_sd_cg, change_n_cg, es.type = "g") %>%
        as.data.frame() %>% dplyr::select(es, se) %>%
        suppressWarnings()})
  }

jitai_es_changeES <- jitai_df_clean %>% 
  changeES()
```

<br>

### Bind effect size data to data seta
```{r}
jitai_df_with_es <- bind_cols(jitai_df_clean, coalesce(jitai_es_meanSD, jitai_es_changeES)) %>% 
  mutate(es = es * -1) # positive g indicates treatment favors ig

jitai_df_with_es %>% 
  select(study, es, outcome_type, post_m_ig, post_m_cg, change_m_ig, change_m_cg) 
```

## Load ROB2

```{r}
jitai_rob <- readxl::read_excel("data/raw/jitai-rob-templat_chs_fv_cyp.xlsx", skip = 1) %>% 
  clean_names() %>% 
  glimpse()
```

```{r}
jitai_rob_renamed <- jitai_rob %>%
  select(id_study = study,
         rob_1_1                    =  x1_1_sg,
         rob_1_1_descr              =  x1_1_description,
         rob_1_2                    =  x1_2_ac,
         rob_1_2_descr              =  x1_2_description,
         rob_1_3                    =  x1_3_bl_imbalance,
         rob_1_3_descr              =  x1_3_description,
         domain_1_rating            =  domain_1_rating,
         rob_2_1                    =  x2_1_participants_aware_allocation,
         rob_2_2                    =  x2_2_personnel_aware_allocation,
         rob_2_3                    =  x2_3_deviations_trial,
         rob_2_3_descr              =  x2_3_description,
         rob_2_4                    =  x2_4_affected_outcome,
         rob_2_4_descr              =  x2_4_description,
         rob_2_5                    =  x2_5_deviations_balanced,
         rob_2_5_descr              =  x2_5_description,
         domain_2_part_1_rating     =  rating_2_1,
         rob_2_6                    =  x2_6_itt_analysis,
         rob_2_6_descr              =  x2_6_description,
         rob_2_7                    =  x2_7_impact,
         rob_2_7_descr              =  x2_7_description,
         domain_2_part_2_rating     =  rating_2_2,
         domain_2_rating            =  domain_2_rating,
         rob_3_1                    =  x3_1_outcome_available,
         rob_3_1_over_cutoff = rob_3_1_over_cutoff,
         attrition                  =  attrition,
         rob_3_2                    =  x3_2_result_unbiased,
         rob_3_2_descr              =  x3_2_description,
         rob_3_4                    =  x3_4_missingness_depends_on_true_value,
         rob_3_4_descr              =  x3_4_description,
         domain_3_rating            =  rating_3,
         rob_4_1                    =  x4_1_outcome_inappropriate,
         rob_4_2                    =  x4_2_measurement_group_differences,
         rob_4_3_sr                 =  x4_3_assessors_aware_self_reported,
         rob_4_3_cr                 =  x4_3_assessors_aware_clinician_rated,
         rob_4_3_descr              =  description_4_3,
         domain_4_rating_sr         =  domain_4_rating_self_reported,
         domain_4_rating_cr         =  domain_4_rating_clinician_rated,
         rob_5_registered_prospective= registered_prospective,
         registration_number,
         rob_5_2                     = rating_dicrepancies,
         rob_5_discrepancies         = discrepancies,
         domain_5_rating             = domain_5_rating,
         overall_score,
         everything()) %>% 
  
  mutate(rob_2_4 = "NI",
         rob_2_5 = "NI")
```

### Apply ROB2 Algorithm 
```{r}
jitai_rob_calculated <- jitai_rob_renamed %>% 
  mutate(
    domain_1_rating_algorithm = case_when(
      rob_1_2 %in% c("Y", "PY") &  rob_1_1 %in% c("Y", "PY", "NI") &  rob_1_3 %in% c("N", "PN", "NI")  ~ "LR",
      rob_1_2 == "NI" &  rob_1_3 %in% c("N", "PN", "NI")   ~ "SC",
      rob_1_2  %in% c("Y", "PY")  & rob_1_1  %in% c("N", "PN")   ~ "SC",
      rob_1_2  %in% c("Y", "PY") &  rob_1_1 %in% c("Y", "PY", "NI") & rob_1_3 %in% c("Y", "PY")   ~ "SC",
      rob_1_2 %in% c("N", "PN") ~ "HR",
      rob_1_2 == "NI" &  rob_1_3 %in% c("Y", "PY") ~ "HR"),
    
    domain_2_rating_algorithm_part_1 = case_when(
      rob_2_1 %in% c("N", "PN") & rob_2_2 %in% c("N", "PN") ~ "LR",
      (rob_2_1 %in% c("Y", "PY", "NI") | rob_2_2 %in% c("Y", "PY", "NI")) & rob_2_3 == "N" ~  "LR",
      (rob_2_1 %in% c("Y", "PY", "NI") | rob_2_2 %in% c("Y", "PY", "NI")) & rob_2_3 == "NI" ~ "SC",
      (rob_2_1 %in% c("Y", "PY", "NI") | rob_2_2 %in% c("Y", "PY", "NI")) & rob_2_3 %in% c("Y", "PY")  & rob_2_4 %in% c("N", "PN") ~ "SC", 
      (rob_2_1 %in% c("Y", "PY", "NI") | rob_2_2 %in% c("Y", "PY", "NI")) & rob_2_3 %in% c("Y", "PY")  & rob_2_4 %in% c("Y", "PY", "NI") & rob_2_5 %in% c("Y", "PY") ~ "SC",
      (rob_2_1 %in% c("Y", "PY", "NI") | rob_2_2 %in% c("Y", "PY", "NI")) & rob_2_3 %in% c("Y", "PY")  & rob_2_4 %in% c("Y", "PY", "NI") & rob_2_5 %in% c("N", "PN", "NI")~ "HR"),
    
    domain_2_rating_algorithm_part_2 = case_when(
      rob_2_6 %in% c("Y", "PY") ~ "LR",
      rob_2_6 %in% c("N", "PN", "NI") & rob_2_7 %in% c("N", "PN") ~ "SC",
      rob_2_6 %in% c("N", "PN", "NI") & rob_2_7 %in% c("Y", "PY", "NI") ~ "HR"),
    
    domain_2_rating_algorithm = case_when(
      domain_2_rating_algorithm_part_1 == "LR" & domain_2_rating_algorithm_part_2 == "LR" ~ "LR",
      domain_2_rating_algorithm_part_1 == "HR" | domain_2_rating_algorithm_part_2 == "HR" ~ "HR",
      domain_2_rating_algorithm_part_1 %in% c("LR", "SC") & domain_2_rating_algorithm_part_2 %in% c("LR", "SC") ~ "SC"),
    
    domain_3_rating_algorithm = case_when(
      rob_3_1 %in% c("Y", "PY")  ~ "LR",
      rob_3_1 %in% c("N", "PN", "NI") & rob_3_2 %in% c("Y", "PY")  ~ "LR",
      # rob_3_1 %in% c("N", "PN", "NI") & rob_3_2 %in% c("N", "PN") & rob_3_3 %in% c("N", "PN") ~ "LR",
      rob_3_1 %in% c("N", "PN", "NI") & rob_3_2 %in% c("N", "PN", "NI", "NA") & # rob_3_3 %in% c("Y", "PY", "NI") & # 3.3 is removed
        rob_3_4 %in% c("N", "PN") ~ "SC",
      rob_3_1_over_cutoff == "Y" ~ "HR",
      rob_3_1 %in% c("N", "PN", "NI") & rob_3_2 %in% c("N", "PN", "NI", "NA") & # rob_3_3 %in% c("Y", "PY", "NI") & 
        rob_3_4 %in% c("Y", "PY", "NI") ~ "HR"), 
    
    domain_4_rating_algorithm_sr = case_when(
      rob_4_3_sr %in% c("Y", "PY")  ~ "HR",
      rob_4_3_sr == "NI"  ~ "SC",
      rob_4_3_sr %in% c("N", "PN")  ~ "LR"),
    
    domain_4_rating_algorithm_cr = case_when(
      rob_4_3_cr %in% c("Y", "PY")  ~ "HR",
      rob_4_3_cr == "NI"  ~ "SC",
      rob_4_3_cr %in% c("N", "PN")  ~ "LR"),
    
    domain_5_rating_algorithm = case_when(
      rob_5_registered_prospective == "Y" & rob_5_2 %in% c("N", "PN") ~ "LR",
      rob_5_registered_prospective == "Y" & rob_5_2 == "Y" ~ "HR",
      rob_5_registered_prospective == "N" ~ "SC"),

    overall_score_algorithm = case_when( 
      domain_1_rating_algorithm == "LR" &  
        domain_2_rating_algorithm == "LR" &  
        domain_3_rating_algorithm == "LR" &  
        domain_4_rating_algorithm_sr == "LR" &  
        #domain_4_rating_algorithm_cr == "LR" |  not relevant for this study
        domain_5_rating_algorithm == "LR" ~  "LR",
      domain_1_rating_algorithm == "HR" |  
        domain_2_rating_algorithm == "HR" |  
        domain_3_rating_algorithm == "HR" |  
        domain_4_rating_algorithm_sr == "HR" |  
        #domain_4_rating_algorithm_cr == "HR" |  not relevant for this study 
        domain_5_rating_algorithm == "HR" ~  "HR",
      TRUE ~ "SC")
  ) %>% 
  select(
    id_study,
    contains("rating_algorithm"),
    overall_score_algorithm,
    -contains("part")
  ) %>% 
  mutate(rob = case_when(
    overall_score_algorithm == "LR" ~ 0,
    overall_score_algorithm == "SC" ~ 1,
    overall_score_algorithm == "HR" ~ 2,
  ))
jitai_rob_calculated
```

<br>

### Join data

```{r}
jitai_cleaned <- full_join(jitai_df_with_es, jitai_rob_calculated) %>% 
  #rename(intervention_type = type_of_intervention_cog_exer_both_bt_pe_pa_phy_at,
  #       control_type = control_condition_tau_wlc_injusted_intervention) %>% 
  mutate(sample_size = case_when(
    is.na(change_n_ig) ~ (post_n_ig + post_n_cg),
    is.na(post_n_ig) ~ (change_n_ig + change_n_cg),
    TRUE ~ (post_n_ig + post_n_cg)
  ),
  id_study = study,
  percent_women = as.numeric(percent_women),
  vi = se^2) 
```

## Adding Pain Disability

```{r}
jitai_pain_disability <- readxl::read_excel("data/raw/JITAI-meta-analysis-template_NUR_disability.xlsx", sheet = "Template") %>% janitor::clean_names() %>% 
  mutate(device = device_supported_vr_smartphone_website,
          sample = ifelse(sample == "co", "completers", sample))


jitai_pain_disability_es <- jitai_pain_disability %>% 
  escalc(m1i = post_m_ig, 
         m2i = post_m_cg,
         sd1i = ifelse(is.na(post_sd_ig), post_se_ig * sqrt(post_n_ig), post_sd_ig),
         sd2i = ifelse(is.na(post_sd_cg), post_se_cg * sqrt(post_n_cg), post_sd_cg),
         n1i = post_n_ig,
         n2i = post_n_cg,
         measure = "SMD",
         data=.) # needs to be an escalc object first
```

## Zhang 1/ a is change 

```{r}
jitai_pain_disability_change <- jitai_pain_disability_es %>% 
  mutate(change_sd_ig = (change_ig_ci_upper -change_ig_ci_lower)/3.92 * sqrt(change_n_ig),
         change_sd_cg = (change_cg_ci_upper -change_cg_ci_lower)/3.92 * sqrt(change_n_ig))

jitai_pd_changeES <- jitai_pain_disability_change %>% 
  changeES()
```

```{r}
jitai_pd_change <- jitai_pain_disability_change %>% 
  mutate(yi = ifelse(id_study == "Zheng1, 2022", -0.7017006, yi),
         vi = ifelse(id_study == "Zheng1, 2022", 0.3438956^2, vi),
         id_study = ifelse(id_study == "Zheng2, 2022", "Zheng, 2022b", id_study),
         id_study = ifelse(id_study == "Zheng1, 2022", "Zheng, 2022a", id_study),
  )
```


```{r}
jitai_pain_disability_avg <- as.data.frame(aggregate(jitai_pd_change, 
                                    cluster = id_study, 
                                    struct="CS" , #compound symmetric structure as nested are not indpendent
                                    rho = .5)) %>% 
  mutate(instrument = ifelse(outc_measure == "pi stress", "pi", outc_measure),
         outcome_measure = "Pain Interference",
         intervention_group = str_replace_all(cond_spec_trt1, 
                                          pattern = c("cbt" = "CBT", "activity" = "Activity")),
         control_group = stringr::str_to_sentence (cond_spec_trt2),
         es = yi*-1) %>%  # reverse coded 
  relocate(id_study, es, vi, intervention_group, control_group, outcome_measure)
```

> Wir haben immer in die Spalte „outcome measure“ die verwendeten Scores für Pain Disabiity / Pain interference dazugeschrieben. Pain disability wurde mittels RMDQ, ODI, mODI oder "pain interference" erhoben. Bei Garcia et al. wurde die "pain interference" mit 1. Activity, 2. Sleep, 3. Mood, 4. Stress erhoben. Ist es möglich von all den vier erhobenen „pain interference" Werten den Durchschnitt zu bilden? Bei Garcia et al. haben wir auch wieder nur den "standard error". 


```{r}
jitai_cleaned_pd <- left_join(jitai_pain_disability_avg, jitai_rob_calculated, by = "id_study") %>% 
  #rename(intervention_type = type_of_intervention_cog_exer_both_bt_pe_pa_phy_at,
  #       control_type = control_condition_tau_wlc_injusted_intervention) %>% 
  mutate(sample_size =  post_n_ig + post_n_cg,
         baseline_m_cg = as.numeric(baseline_m_cg),
         clbp_diagnosis_cutoff = as.character(clbp_diagnosis_cutoff),
         study_label = paste0(id_study, " - ", outcome_measure),
         study_title = study) 

jitai_cleaned_pd %>% glimpse()
```

<br>

### Join Intensity, Catastrophizing, and Interference

```{r}
jitai_cleaned_pi_pc_pd <- bind_rows(jitai_cleaned, jitai_cleaned_pd) %>% relocate(id_study, study_label, es, se, yi, vi, rob) %>% drop_na(id_study)
jitai_cleaned_pi_pc_pd 
```

## Average data

### Pain Intensity
```{r, warning=FALSE, message =FALSE}
jitai_pi_raw <- jitai_cleaned_pi_pc_pd %>% 
  filter(outcome_measure == "Pain Intensity") 

#### Aggregate Studies with multiple ES (Özden, 2021 and Irvine 2015)
jitai_pi_es <- jitai_pi_raw %>% #### Aggregate Studies with multiple ES (Özden, 2021 and Irvine 2015)
  escalc(yi=es, sei=se, data=.) # needs to be an escalc object first

jitai_pi_avg <- as.data.frame(aggregate(jitai_pi_es, 
                                    cluster = study, 
                                    struct="CS" , #compound symmetric structure as nested are not indpendent
                                    rho = .5))  %>% 
  mutate(control_group = case_when(
    study == "Irvine, 2015" ~ "Active + Inactive",
    TRUE ~ control_group
  ))

intensity <- jitai_pi_avg
```

### Pain Catastrophizing
```{r}
jitai_pc_raw <- jitai_cleaned_pi_pc_pd %>% 
  filter(outcome_measure == "Pain Catastrophizing") %>% 
  mutate(control_group = case_when(
    study == "Irvine, 2015" ~ "Active + Inactive", # this will be aggregated in the next step
    TRUE ~ control_group
  ))

#### Aggregate Data

jitai_pc_es <- jitai_pc_raw %>% 
  escalc(yi=es, sei=se, data=.)

jitai_pc_avg <- as.data.frame(aggregate(jitai_pc_es, 
                                  cluster = study,
                                  struct="CS" , #compound symmetric structure as nested are not indpendent
                                  rho = 0.5))

catastrophizing <- jitai_pc_avg
```


```{r}
catastrophizing %>% 
  kableExtra::kbl() %>% 
  kableExtra::kable_styling("striped", full_width = F) %>%
  kableExtra::scroll_box(width = "100%", height = "400px")
```

## Pain Interference

```{r}
interference <- jitai_cleaned_pd
```

## All Data
```{r}
jitai_data <- bind_rows(intensity, catastrophizing, interference) %>% 
  mutate(
  risk_of_bias = case_when(
    overall_score_algorithm == "LR" ~ "Low",
    overall_score_algorithm == "SC" ~ "Some concern",
    overall_score_algorithm == "HR" ~ "High")) %>% 
  select(id_study, es, vi, 
         "Pain Dimension" = outcome_measure, 
         rob, risk_of_bias,
         intervention_group:sr_clinician,
         outcome_type:control_type,
         everything()) 
```

## Save data used in meta-analysis

```{r}
write_csv(jitai_data, "data/tidy/jitai_data.csv")
```

# Exploratory data analysis

```{r}
skim(jitai_data)
```


# Used resoures

- [Formulas](https://handbook-5-1.cochrane.org/chapter_7/7_7_3_2_obtaining_standard_deviations_from_standard_errors_and.htm)

