---
title: "JITAI Meta-Analysis"
author: "Constantin Yves Plessen"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    pandoc_args:
    - +RTS
    - "-K512m"
    - "-RTS"
    code_folding: show
    highlight: pygment
    keep_md: no
    theme: lumen
    toc: yes
    toc_depth: 3
    toc_float: yes
  word_document:
    toc: yes
    toc_depth: '3'
  pdf_document:
    toc: yes
    toc_depth: '3'
subtitle: 2. Main Analyses
editor_options:
  chunk_output_type: console
---



```{r setup, include=FALSE}
stack_size <- getOption("pandoc.stack.size", default = "512m")
knitr::opts_chunk$set(echo = TRUE)
library(weightr)
library(RoBMA)
library(metafor)
library(dmetar)
library(metaviz)
library(meta)
library(metapsyTools)
library(tidyverse)
library(robvis)

# Bayesian MA
library(brms)
library(ggridges)
library(tidybayes)
library(dplyr)
library(ggplot2)
library(ggridges)
library(glue)
library(stringr)
library(forcats)

# helper function
PET.PEESE <- function(data) {
  mod <- list()
  fit_PET <- lm(yi ~ sqrt(vi), 
                weights = 1/vi, 
                data = data)
  
  pet_p <- coef(summary(fit_PET))["(Intercept)", "Pr(>|t|)"] # pet p-value < .10 -> peese
  
  if(pet_p >= .1) {
    mod$b <- coef(summary(fit_PET))["(Intercept)", "Estimate"] # pet estimate
    mod$ci.lb <- confint(fit_PET)["(Intercept)", "2.5 %"] 
    mod$ci.ub<- confint(fit_PET)["(Intercept)", "97.5 %"] 
    mod$pval <- pet_p
    mod$type <- "PET"
    
  }else{
    
    fit_PEESE <- lm(yi ~ vi, 
                    weights = 1/vi, 
                    data = data)
    
    mod$pval <- coef(summary(fit_PEESE))["(Intercept)", "Pr(>|t|)"] # pet p-value < .10 -> peese
    mod$b  <- coef(summary(fit_PEESE))["(Intercept)", "Estimate"] # peese estimate
    mod$ci.lb <- confint(fit_PEESE)["(Intercept)", "2.5 %"] 
    mod$ci.ub <- confint(fit_PEESE)["(Intercept)", "97.5 %"] 
    mod$type <- "PEESE"

  }
  return(mod)
}

rob_append_weights <- function(data, res){

  if (!("rma" %in% class(res))) {
    stop("Result objects need to be of class \"meta\" - output from metafor package functions")
  }

  # Extract weights
  weights <- data.frame(id_study = names(stats::weights(res)),
                        weight = stats::weights(res),
                        row.names = NULL)

  # Merge by Study name to create new dataframe
  rob_df <- dplyr::left_join(data, weights, by = "id_study")

  # Employ check to see if data has merged properly If a merge has failed, one
  # of the Weight cells will be NA, meaning the sum will also be NA
  if (is.na(sum(rob_df$weight))) {
    stop(paste0("Problem with matching - weights do not equal 100. ",
                "Check that the names of studies are the same in the ROB ",
                "data and the resobject (stored in slab)"))
  }

  return(rob_df)
}
```

# Overview of Document

This document entails all analyses conducted for the JITAI meta-analysis and follows the structure of the preregistration:

1. Meta-analytic methods

Meta-analytic methods will be used to estimate pooled effect sizes based on the results of studies that use comparable interventions, controls and outcome measures. A random effects model will be used with standardized mean differences on the continuous outcomes described above, such as self-report measures of pain intensity. Heterogeneity will be assessed with I-squared statistics, where a value greater than 50% suggests substantial heterogeneity. 

2. Publication Bias Assessment

3. Sensitivity analyses

Sensitivity analyses based on study quality will also be performed, along with tests of publication bias using funnel plots, Eggers Regression test, precision-effect estimate with standard errors (PET-PEESE), and p-curve analysis. 

4. Analysis of subgroups or subsets 

Where sufficient data are available sub-group analysis will be performed based on 
- type of control condition
- type of intervention
- gender. 

We initially planned to only conduct subgroup analysis if a power analysis indicates sufficient statistical power of subgroup analyses. We did not reach sufficient statistical power, we however conducted the analyses and report the results as exploratory analyses.

<br>

# 1. Data Cleaning

## Load Data
```{r, warning=FALSE, message =FALSE}
jitai_data <- read_csv("data/tidy/jitai_data.csv") %>% 
  mutate(se = sqrt(vi))
jitai_data$control_group <- str_replace(jitai_data$control_group, " Control", "")
jitai_data$intervention_group <- str_replace(jitai_data$intervention_group, "Activity", "Exercise")

intensity <- jitai_data %>% 
  filter(`Pain Dimension` == "Pain Intensity") 

catastrophizing <- jitai_data %>% 
  filter(`Pain Dimension` == "Pain Catastrophizing") 

interference <- jitai_data %>% 
  filter(`Pain Dimension` == "Pain Interference") 
```


# 2. All Pain Domains

Here are analyses including all Pain Domains: Pain Intensity, Pain Catastrophizing, and Pain Disability/Interference

## Main Analysis
```{r}
pi_pc_pd_result <- meta::metagen(data = jitai_data,
                              TE = es, 
                              seTE = sqrt(vi), 
                              subgroup = `Pain Dimension`,
                              studlab = id_study,
                              sm = "g", 
                              hakn = TRUE, 
                              method.tau = "REML", 
                              prediction = TRUE, 
                              random = TRUE,
                              common = FALSE)

pi_pc_pd_result
```

## Analyses with other R packages

```{r}
pi_pc_pd_metapsytools <- runMetaAnalysis(jitai_data,
                method.tau = "REML",
                hakn = TRUE,
               # study.var = "id_study", # brakes subgroup analyses for 3lvl models
                extra.grouping.var = NULL,
                arm.var.1 = "intervention_group",
                arm.var.2 = "control_group",
                measure.var = "outcome_measure",
                es.var = "es",
                se.var = "se",
                low.rob.filter = "rob < 1",
                method.tau.ci = "Q-Profile",
                round.digits = 2,
                which.outliers = "combined",
                which.influence = "combined",
                which.rob = "combined",
                nnt.cer = 0.2,
                rho.within.study = 0.5,
                use.rve = TRUE,
                html = TRUE)

pi_pc_pd_metafor <- rma( data = jitai_data,
                         yi = es, 
                         vi = vi, 
                         slab = id_study,
                         method = "REML", 
                         test = "knha") 

```


<br>

## Plots

### Forest Plot
```{r height = 13}
meta::forest(pi_pc_pd_result,
             subgroup = TRUE,
             weigth = TRUE,
            # layout = "JAMA",
            leftcols = c("id_study", "intervention_group", "control_group", "risk_of_bias"),
            leftlabs = c("Author", "Intervention", "Control", "Risk of Bias"))
```

Saving plot
```{r}
pdf(file = "figures/pi_pc_pd_forest.pdf",    # The directory you want to save the file in
    width = 13, # The width of the plot in inches
    height = 10) # The height of the plot in inches

meta::forest(pi_pc_pd_result,
             subgroup = TRUE,
             weigth = TRUE,
            # layout = "JAMA",
            leftcols = c("id_study", "intervention_group", "control_group", "risk_of_bias"),
            leftlabs = c("Author", "Intervention", "Control", "Risk of Bias"))

dev.off()
```

<br>

### Funnel Plot

```{r}
pi_metafor <- rma(data = intensity,
                  yi = es, 
                  vi = vi, 
                  slab = id_study,
                  method = "REML", 
                  test = "knha") 

pc_metafor <- rma(data = catastrophizing,
                  yi = es, 
                  vi = vi, 
                  slab = id_study,
                  method = "REML", 
                  test = "knha")  

pd_metafor <- rma(data = interference,
                  yi = es, 
                  vi = vi, 
                  slab = id_study,
                  method = "REML", 
                  test = "knha") 

funnel(pi_metafor, main="Pain Intensity")
funnel(pc_metafor, main="Pain Catastrophizing")
funnel(pd_metafor, main="Pain Interference")
```


Saving Plots
```{r}
pdf(file = "figures/pi_pc_pd_funnel.pdf",    # The directory you want to save the file in
    width = 5, # The width of the plot in inches
    height = 8) # The height of the plot in inches

### set up 2x2 array for plotting
par(mfrow=c(3,1))
 
### draw funnel plots
funnel(pi_metafor, main="Pain Intensity")
funnel(pc_metafor, main="Pain Catastrophizing")
funnel(pd_metafor, main="Pain Interference")
dev.off()
```

#### Contour Enhanced Funnel Plot
```{r}
### draw funnel plots
funnel(pi_metafor, main="Pain Interference", 
       level=c(90, 95, 99), shade=c("white", "gray55", "gray75"), 
       refline=0, 
       legend=TRUE)

funnel(pc_metafor, main="Pain Catastrophizing", level=c(90, 95, 99), 
       shade=c("white", "gray55", "gray75"), 
       refline=0, 
       legend=TRUE)

funnel(pd_metafor, main="Pain Interference", level=c(90, 95, 99), 
       shade=c("white", "gray55", "gray75"), 
       refline=0, 
       legend=TRUE)
```


```{r}
pdf(file = "figures/pi_pc_pd_funnel_contour.pdf",    # The directory you want to save the file in
    width = 8, # The width of the plot in inches
    height = 8) # The height of the plot in inches

par(mfrow=c(3,1))
 
### draw funnel plots
funnel(pi_metafor, main="Pain Interference", 
       level=c(90, 95, 99), shade=c("white", "gray55", "gray75"), 
       refline=0, 
       legend=TRUE)

funnel(pc_metafor, main="Pain Catastrophizing", level=c(90, 95, 99), 
       shade=c("white", "gray55", "gray75"), 
       refline=0, 
       legend=TRUE)

funnel(pd_metafor, main="Pain Interference", level=c(90, 95, 99), 
       shade=c("white", "gray55", "gray75"), 
       refline=0, 
       legend=TRUE)
dev.off()
```

#### With Trim-and-Fill Method
```{r}
taf.pi <- trimfill(pi_metafor)
taf.pc <- trimfill(pc_metafor)
taf.pd <- trimfill(pd_metafor)

funnel(taf.pi, main="Pain Interference", 
       level=c(90, 95, 99), shade=c("white", "gray55", "gray75"), 
       refline=0, 
       legend=TRUE)

funnel(taf.pc, main="Pain Catastrophizing", level=c(90, 95, 99), 
       shade=c("white", "gray55", "gray75"), 
       refline=0, 
       legend=TRUE)

funnel(taf.pd, main="Pain Interference", level=c(90, 95, 99), 
       shade=c("white", "gray55", "gray75"), 
       refline=0, 
       legend=TRUE)
```

Saving Plots
```{r}
pdf(file = "figures/pi_pc_pd_funnel_taf.pdf",    # The directory you want to save the file in
    width = 8, # The width of the plot in inches
    height = 8) # The height of the plot in inches

par(mfrow=c(3,1))
 
### draw funnel plots
funnel(taf.pi, main="Pain Interference", 
       level=c(90, 95, 99), shade=c("white", "gray55", "gray75"), 
       refline=0, 
       legend=TRUE)

funnel(taf.pc, main="Pain Catastrophizing", level=c(90, 95, 99), 
       shade=c("white", "gray55", "gray75"), 
       refline=0, 
       legend=TRUE)

funnel(taf.pd, main="Pain Interference", level=c(90, 95, 99), 
       shade=c("white", "gray55", "gray75"), 
       refline=0, 
       legend=TRUE)
dev.off()
```

### *p*-Curve

```{r, error=TRUE}
jitai_data %>% 
  select(TE = es,
         seTE = se,
         studlab = id_study) %>% 
pcurve(.)
```


## Tables

### Study Overview

```{r, warning=FALSE, message =FALSE, results='asis'}
createStudyTable(jitai_data,
                 ## COLUMNS --------------------------------------
                 # Simply add columns in the order in which
                 # they should appear in the table
                 id_study, 
                 `Pain Dimension`,
                 intervention_group,
                 control_group,
                 country, 
                 mean_age, 
                 percent_women,
                 format, 
                 app_compatible_y_n, 
                 # device_supported_virtual_app_web,
                 overall_score_algorithm,
                 #rob2_1_randomization,
                 #rob2_2_deviations,
                 #rob2_3_missing,
                 #rob2_4_measurement,
                 #rob2_5_selection,
                 duration_of_intervention,
                 post_n_ig,
                 post_n_cg,
                 
             #    # You can directly recode values within a variable
             #    arm_format_trt1 = c("CBT" = "cbt", 
             #                        "PST" = "pst",
             #                        "BA" = "bat"),
             #    arm_format_trt2 = c("Wait-List" = "wl", 
             #                        "Care-As-Usual" = "cau"),
             #    n_sessions_trt1, Post_N_trt1, Post_N_trt2, 
             #    country = c("Europe" = "3", "USA" = "1",
             #                "Asia" = "6", "Middle East" = "7", 
             #                "Australia" = "5"),
             #    sg, ac, ba, itt,
             #    
             #    
             #    ## SPECIFICATIONS -------------------------------
             #    # .round.by.digits controls the number of rounded digits for
             #    # specified columns
             #    .round.by.digits = list(mean_age_trt1 = 0, 
             #                            Post_N_trt1 = 0,
             #                            Post_N_trt2 = 0),
                 
                 # .column.names allows to rename columns
                 .column.names = list(id_study = "Study",
                                      country = "Country",
                                      mean_age = "Mean age",
                                      percent_women = "% female",
                                      intervention_group = "Intervention",
                                      control_group = "Control",
                                      duration_of_intervention = "Duration",
                                      format = "Format",
                                      app_compatible_y_n = "App Compatibility",
                                      device = "Device",
                                      n_sessions_trt1 = "Sessions",
                                      overall_score_algorithm = "Risk of Bias",
                                      post_n_ig = "N Intervention", 
                                      post_n_cg = "N Control"))

```

### Effect Sizes
```{r, warning=FALSE, message =FALSE, results='asis'}
pi_pc_pd_metapsytools
```

### Publication Bias Estimates

Trim-and-fill method, limit meta-analysis, selection model correct for publication bias as described here: 

```{r, warning=FALSE, message =FALSE, results='asis'}
metapsyTools::correctPublicationBias(pi_pc_pd_metapsytools,
                                     selmodel.steps = .025)

correctPublicationBias(pi_pc_pd_metapsytools) %>% plot("selection")
```

#### Additional Correction for Publication Bias: PET-PEESE

```{r}
all_pet_peese <- PET.PEESE(jitai_data)

all_pet_peese
```

PET-PEESE adjusts for the relationship between effect sizes and standard errors. If the test for the effect size with PET is not significant at $\alpha = .10$, we interpret the PET model. However, if the test for effect size were significant, we fit and interpret the PEESE model. Using `r all_pet_peese$type`, the corrected estimate is `r all_pet_peese$b`, 95% CI [`r all_pet_peese$ci.lb`, `r all_pet_peese$ci.ub`], *p* = `r round(all_pet_peese$pval, 3)`.

<br>

### Robust Bayesian MA


```{r}

jitai_data <- jitai_data %>% 
  mutate(sample_size = case_when(
   !is.na(post_n_cg) ~ post_n_cg + post_n_ig,
   id_study == "Zheng, 2022a" ~ 37))

fit_RoBMA <- RoBMA(d = jitai_data$es, 
                   n = jitai_data$sample_size, 
                   seed = 1, 
                   model = "PSMA", 
                   parallel = TRUE)

summary(fit_RoBMA)

interpret(fit_RoBMA, output_scale = "cohens_d")
```


## Subgroup analyses

We conducted subgroup analyses for:  
- intervention group  
- control group  
- sample  
- format  
- overall_score_algorithm  

### Control Condition

```{r, warning=FALSE, message =FALSE, results='asis'}
pi_pc_pd_control <- subgroupAnalysis(pi_pc_pd_metapsytools, 
                               .which.run = "combined",
                               control_group) #after package update not working
pi_pc_pd_control
```

### Intervention
```{r, warning=FALSE, message =FALSE, results='asis'}
pi_pc_pd_intervention <- subgroupAnalysis(pi_pc_pd_metapsytools, 
                                    intervention_group,
                                    .which.run = "combined",
                                    .tau.common = TRUE)
pi_pc_pd_intervention
```

### Sample
```{r, warning=FALSE, message =FALSE, results='asis'}
pi_pc_pd_sample <- subgroupAnalysis(pi_pc_pd_metapsytools, 
                              sample,
                              .which.run = "combined",
                              .tau.common = TRUE)
pi_pc_pd_sample
```

### Format
```{r, warning=FALSE, message =FALSE, results='asis'}
pi_pc_pd_format <- subgroupAnalysis(pi_pc_pd_metapsytools, 
                              format,
                              .which.run = "combined",
                              .tau.common = TRUE)
pi_pc_pd_format
```

### Device
```{r, warning=FALSE, message =FALSE, results='asis'}
pi_pc_pd_device <- subgroupAnalysis(pi_pc_pd_metapsytools, 
                             device,
                             .which.run = "combined",
                             .tau.common = TRUE)
pi_pc_pd_device
```

### Risk of Bias
```{r, warning=FALSE, message =FALSE, results='asis'}
pi_pc_pd_rob <- subgroupAnalysis(pi_pc_pd_metapsytools, 
                           overall_score_algorithm,
                           .which.run = "combined",
                           .tau.common = TRUE)
pi_pc_pd_rob
```


<br>

# 3. Risk of Bias: Trafic Light Plot
```{r}
data_rob <- intensity %>% 
 # separate(study, c("author", "year"), sep = ",") %>% 
  select(id_study,
         D1 = domain_1_rating_algorithm,
         D2 = domain_2_rating_algorithm, 
         D3 = domain_3_rating_algorithm, 
         D4 = domain_4_rating_algorithm_sr,
         D5 = domain_5_rating_algorithm, 
         Overall = overall_score_algorithm
  ) %>% 
  mutate_at(vars(2:7),
  ~recode(.,
    "LR"= "Low", 
    "SC"= "Some concerns",
    "HR"= "High")) %>% 
  group_by(id_study) %>% 
  slice(1)

rob_traffic_light(data_rob,
            tool = "ROB2",
            psize = 15)
```

### Weighted ROB Plot

```{r}
pi_rob <- rob_append_weights(data_rob, pi_metafor)

rob_summary(pi_rob,
            tool = "ROB2")
```

<br>

# 4. Automated Reporting with metafor

Cannot be knitted within an RMD file, needs to be executed as a chunk.

This is used for citation purposes.
```{r}
#reporter(pi_pc_pd_metafor, dir = "/Users/cyp/Documents/projects #/work/current/project-4-jitai/2-github/jitai/reporter")
#
#reporter(pi_metafor, dir = "/Users/cyp/Documents/projects /work/current/project-4-jitai/2-github/jitai/reporter")
#
#reporter(pc_metafor, dir = "/Users/cyp/Documents/projects /work/current/project-4-jitai/2-github/jitai/reporter")
#
#reporter(pd_metafor, dir = "/Users/cyp/Documents/projects /work/current/project-4-jitai/2-github/jitai/reporter")
```

<br>
